Testing Gravity Using Type Ia Supernovae Discovered by Next Generation Wide Field Imaging Surveys

### 2019-03-06 doc/article.tex
get more into white paper format

\documentclass{aastex62}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{graphicx}				% Use pdf, png, jpg, or epsÂ§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb,amsmath}
\usepackage{natbib,verbatim}
%\usepackage{grffile}
%\usepackage{textcase}
\usepackage{hyperref}
%\usepackage[overload]{textcase}

@@

\textbf{Co-authors:} (names and institutions)
  \linebreak

\textbf{Endorsers:} (names and institutions)
  \linebreak
 Behzad Ansarinejad $^{1,2}$, 
 Robert Armstrong $^{}$, 
 Carlo Baccigalupi $^{3,4,5}$, 
 Maciej Bilicki $^{6}$, 
 Julian Borrill $^{7}$, 
 Simone Ferraro $^{7}$, 
 Llu\'is Galbany $^{8}$, 
 Juan Garc\'ia-Bellido $^{9}$, 
 Juan Garc\'ia-Bellido $^{10}$, 
 Martina Gerbino $^{}$, 
 Mandeep S.S. Gill $^{11,12,13}$, 
 Larry Gladney $^{14}$, 
 Marc Kamionkowski $^{1,19}$, 
 Kazuya Koyama $^{20}$, 
 Michele Liguori $^{21}$, 
 Joel Meyers $^{22}$, 
 "Surhud More" $^{23}$, 
 Jeffrey A. Newman $^{8}$, 
 Gustavo Niz $^{24}$, 
 "Antonella Palmese" $^{25}$, 
 Francesco Piacentini $^{26}$, 
 Francesco Piacentni  $^{26,27}$, 
 Steven Rodney $^{28}$, 
 Benjamin Rose $^{29}$, 
 Lado Samushia $^{30}$, 
 Neelima Sehgal $^{31}$, 
 Leonardo Senatore $^{11}$, 
 Huanyuan Shan $^{1,33}$, 
 Scott Watson $^{35}$, 
 Martin White $^{36,7}$, 
 Weishuang Xu $^{37}$, 
 Gong-Bo Zhao $^{38,39,20}$,

@@

\title{Testing Gravity Using Type Ia Supernovae Discovered by Next Generation Wide Field Imaging Surveys}
\author[0000-0001-6315-8743]{A.~G.~Kim}
\affiliation{Physics Division, Lawrence Berkeley National Laboratory, 
\author{G.~Aldering}
\affiliation{Physics Division, Lawrence Berkeley National Laboratory, 
\author{P.~Antilogus}
\affiliation{Laboratoire de Physique Nucl\'eaire et de Hautes Energies, Sorbonne Universit\'e, CNRS-IN2P3, 4 Place Jussieu, 75005 Paris, France}    
\author{A.~Bahmanyar}
\affiliation{Department of Astronomy and Astrophysics, University of Toronto,
\author{S.~BenZvi}
\affiliation{Department of Physics and Astronomy, University of Rochester, Rochester, NY 14627, USA}
\author{H.~Courtois}
\affiliation{Universit\'e de Lyon, F-69622, Lyon, France; Universit\'e de Lyon
\author{T.~Davis}
\affiliation{School of Mathematics and Physics, University of Queensland, Brisbane, QLD 4072, Australia}
\author{S.~Gontcho A Gontcho}
\affiliation{Department of Physics and Astronomy, University of Rochester, Rochester, NY 14627, USA}
\author{O.~Graur}
\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY 10024, USA}
\affiliation{NSF Astronomy and Astrophysics Postdoctoral Fellow}
\author{R.~Graziani}
\affiliation{Universit\'e Clermont Auvergne, CNRS/IN2P3, Laboratoire de
\author{C.~Harper}
\affiliation{Physics Division, Lawrence Berkeley National Laboratory, 
\author{R.~Hlo\u{z}ek}
\affiliation{Department of Astronomy and Astrophysics, University of Toronto,
\affiliation{Dunlap Institute for Astronomy and Astrophysics, University of Toronto, ON, M5S 3H4}
\author{C.~Howlett}
\affiliation{International Centre for Radio Astronomy Research, The University of Western Australia, Crawley, WA 6009, Australia}
\author{D.~Huterer}
\affiliation{Department of Physics, University of Michigan, 450 Church Street, Ann
\author{C.~Ju}
\affiliation{Physics Division, Lawrence Berkeley National Laboratory, 
\author{P.-F.~Leget}
\affiliation{Laboratoire de Physique Nucl\'eaire et de Hautes Energies, Sorbonne Universit\'e, CNRS-IN2P3, 4 Place Jussieu, 75005 Paris, France}    
\author{E.~V.~Linder}
\affiliation{Physics Division, Lawrence Berkeley National Laboratory, 
\author{P.~McDonald}
\affiliation{Physics Division, Lawrence Berkeley National Laboratory, 
\author{J.~Nordin}
\affiliation{Institut fur Physik, Humboldt-Universitat zu Berlin, Newtonstr. 15, 12489 Berlin, Germany}
\author{P.~Nugent}
\affiliation{Computational Research Division, Lawrence Berkeley National Laboratory, 
    1 Cyclotron Road, Berkeley, CA, 94720}\author{S.~Perlmutter}
\affiliation{Physics Division, Lawrence Berkeley National Laboratory, 
\affiliation{Department of Physics, University of California Berkeley, 366 LeConte Hall MC 7300, Berkeley, CA, 94720-7300}
\author{N.~Regnault}
\affiliation{Laboratoire de Physique Nucl\'eaire et de Hautes Energies, Sorbonne Universit\'e, CNRS-IN2P3, 4 Place Jussieu, 75005 Paris, France}    
\author{M.~Rigault}
\affiliation{Universit\'e de Lyon, F-69622, Lyon, France; Universit\'e de Lyon
\author{A.~Shafieloo}
\affiliation{Korea Astronomy and Space Science Institute, Yuseong-gu, Daedeok-daero 776, Daejeon 34055, Korea}
\author{A.~Slo\u{z}ar}
\affiliation{Brookhaven National Laboratory, Physics Department, Upton, NY
\author{others}

@@

\begin{abstract}
In the upcoming decade cadenced wide-field imaging surveys 
will increase the number of identified  $z<0.3$ Type~Ia supernovae (SNe~Ia)  from the hundreds to the
hundreds of thousands.  The increase in the number density  and solid-angle coverage 
of SNe~Ia, in parallel with improvements in the standardization of
their absolute magnitudes, now make them competitive probes of the growth of structure and hence of gravity.  The peculiar velocity power spectrum
is sensitive to $\gamma$, which captures the effect of gravity on the linear growth of structure through the relation $f=\Omega_M^\gamma$.
In the next decade the peculiar velocities of
SNe~Ia in the local $z<0.3$ Universe will provide a measure of $\gamma$ with as low as
$0.01$ precision that can definitively distinguish  between General Relativity and leading models of alternative gravity.
\end{abstract}

>>>>

\documentclass{aastex62}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{graphicx}				% Use pdf, png, jpg, or epsÂ§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb,amsmath}
\usepackage{natbib,verbatim}
\usepackage[multiple]{footmisc}
%\usepackage{grffile}
%\usepackage{textcase}
\usepackage{hyperref}

%\usepackage[overload]{textcase}

@@

\textbf{Co-authors:}
%\author[0000-0001-6315-8743]{A.~G.~Kim}
%\affiliation{Physics Division, Lawrence Berkeley National Laboratory, 
%    1 Cyclotron Road, Berkeley, CA, 94720}
G.~Aldering\footnotemark[1],
\footnotetext[1]{Physics Division, Lawrence Berkeley National Laboratory, 
P.~Antilogus\footnotemark[2],
\footnotetext[2]{Laboratoire de Physique Nucl\'eaire et de Hautes Energies, Sorbonne Universit\'e, CNRS-IN2P3, 4 Place Jussieu, 75005 Paris, France}    
A.~Bahmanyar\footnotemark[3],
\footnotetext[3]{Department of Astronomy and Astrophysics, University of Toronto,
S.~BenZvi\footnotemark[4],
\footnotetext[4]{Department of Physics and Astronomy, University of Rochester, Rochester, NY 14627, USA}
H.~Courtois\footnotemark[5],
\footnotetext[5]{Universit\'e de Lyon, F-69622, Lyon, France; Universit\'e de Lyon
T.~Davis\footnotemark[6],
\footnotetext[6]{School of Mathematics and Physics, University of Queensland, Brisbane, QLD 4072, Australia}
S.~Gontcho A Gontcho\footnotemark[4],
%\affiliation{Department of Physics and Astronomy, University of Rochester, Rochester, NY 14627, USA}
O.~Graur\footnotemark[7]\textsuperscript{,}\footnotemark[8]\textsuperscript{,}\footnotemark[9],
\footnotetext[7]{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA}
\footnotetext[8]{Department of Astrophysics, American Museum of Natural History, New York, NY 10024, USA}
\footnotetext[9]{NSF Astronomy and Astrophysics Postdoctoral Fellow}
R.~Graziani\footnotemark[10],
\footnotetext[10]{Universit\'e Clermont Auvergne, CNRS/IN2P3, Laboratoire de
C.~Harper\footnotemark[1],
%\affiliation{Physics Division, Lawrence Berkeley National Laboratory, 
%    1 Cyclotron Road, Berkeley, CA, 94720}
R.~Hlo\u{z}ek\footnotemark[3]\textsuperscript{,}\footnotemark[11],
%\affiliation{Department of Astronomy and Astrophysics, University of Toronto,
%50 St. George Street, Toronto, Ontario, Canada M5S 3H4}
\footnotetext[11]{Dunlap Institute for Astronomy and Astrophysics, University of Toronto, ON, M5S 3H4}
C.~Howlett\footnotemark[12],
\footnotetext[12]{International Centre for Radio Astronomy Research, The University of Western Australia, Crawley, WA 6009, Australia}
D.~Huterer\footnotemark[13],
\footnotetext[13]{Department of Physics, University of Michigan, 450 Church Street, Ann
C.~Ju\footnotemark[12],
%\affiliation{Physics Division, Lawrence Berkeley National Laboratory, 
%    1 Cyclotron Road, Berkeley, CA, 94720}
P.-F.~Leget\footnotemark[14],
\footnotetext[14]{Laboratoire de Physique Nucl\'eaire et de Hautes Energies, Sorbonne Universit\'e, CNRS-IN2P3, 4 Place Jussieu, 75005 Paris, France}    
E.~V.~Linder\footnotemark[1],
%\affiliation{Physics Division, Lawrence Berkeley National Laboratory, 
%    1 Cyclotron Road, Berkeley, CA, 94720}
P.~McDonald\footnotemark[1],
%\affiliation{Physics Division, Lawrence Berkeley National Laboratory, 
%    1 Cyclotron Road, Berkeley, CA, 94720}
J.~Nordin\footnotemark[15],
\footnotetext[15]{Institut fur Physik, Humboldt-Universitat zu Berlin, Newtonstr. 15, 12489 Berlin, Germany}
P.~Nugent\footnotemark[16],
\footnotetext[16]{Computational Research Division, Lawrence Berkeley National Laboratory, 
S.~Perlmutter\footnotemark[1],
N.~Regnault\footnotemark[14],
%\affiliation{Laboratoire de Physique Nucl\'eaire et de Hautes Energies, Sorbonne Universit\'e, CNRS-IN2P3, 4 Place Jussieu, 75005 Paris, France}    
M.~Rigault\footnotemark[5],
%\affiliation{Universit\'e de Lyon, F-69622, Lyon, France; Universit\'e de Lyon
%1, Villeurbanne; CNRS/IN2P3, Institut de Physique Nucléaire de
%Lyon, France} 
A.~Shafieloo\footnotemark[17],
\footnotetext[17]{Korea Astronomy and Space Science Institute, Yuseong-gu, Daedeok-daero 776, Daejeon 34055, Korea}
A.~Slo\u{z}ar\footnotemark[18],
\footnotetext[18]{Brookhaven National Laboratory, Physics Department, Upton, NY
M.~Wood-Vasey\footnotemark[19]
\footnotetext[19]{PITT PACC, Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, PA 15260, USA} 
\linebreak

\textbf{Endorsers:}
 Behzad Ansarinejad $^{1,2}$, 
 Robert Armstrong $^{}$, 
 Carlo Baccigalupi $^{3,4,5}$, 
 Maciej Bilicki $^{6}$, 
 Julian Borrill $^{7}$, 
 Simone Ferraro $^{7}$, 
 Llu\'is Galbany $^{8}$, 
 Juan Garc\'ia-Bellido $^{9}$, 
 Juan Garc\'ia-Bellido $^{10}$, 
 Martina Gerbino $^{}$, 
 Mandeep S.S. Gill $^{11,12,13}$, 
 Larry Gladney $^{14}$, 
 Marc Kamionkowski $^{1,19}$, 
 Kazuya Koyama $^{20}$, 
 Michele Liguori $^{21}$, 
 Joel Meyers $^{22}$, 
 "Surhud More" $^{23}$, 
 Jeffrey A. Newman $^{8}$, 
 Gustavo Niz $^{24}$, 
 "Antonella Palmese" $^{25}$, 
 Francesco Piacentini $^{26}$, 
 Francesco Piacentni  $^{26,27}$, 
 Steven Rodney $^{28}$, 
 Benjamin Rose $^{29}$, 
 Lado Samushia $^{30}$, 
 Neelima Sehgal $^{31}$, 
 Leonardo Senatore $^{11}$, 
 Huanyuan Shan $^{1,33}$, 
 Scott Watson $^{35}$, 
 Martin White $^{36,7}$, 
 Weishuang Xu $^{37}$, 
 Gong-Bo Zhao $^{38,39,20}$
  \linebreak

@@

%\title{Testing Gravity Using Type Ia Supernovae Discovered by Next Generation Wide Field Imaging Surveys}
%\author[0000-0001-6315-8743]{A.~G.~Kim}
%\affiliation{Physics Division, Lawrence Berkeley National Laboratory, 
%    1 Cyclotron Road, Berkeley, CA, 94720}
%\author{G.~Aldering}
%\affiliation{Physics Division, Lawrence Berkeley National Laboratory, 
%    1 Cyclotron Road, Berkeley, CA, 94720}
%\author{P.~Antilogus}
%\affiliation{Laboratoire de Physique Nucl\'eaire et de Hautes Energies, Sorbonne Universit\'e, CNRS-IN2P3, 4 Place Jussieu, 75005 Paris, France}    
%\author{A.~Bahmanyar}
%\affiliation{Department of Astronomy and Astrophysics, University of Toronto,
%50 St. George Street, Toronto, Ontario, Canada M5S 3H4}
%\author{S.~BenZvi}
%\affiliation{Department of Physics and Astronomy, University of Rochester, Rochester, NY 14627, USA}
%\author{H.~Courtois}
%\affiliation{Universit\'e de Lyon, F-69622, Lyon, France; Universit\'e de Lyon
%1, Villeurbanne; CNRS/IN2P3, Institut de Physique Nucléaire de
%Lyon, France} 
%\author{T.~Davis}
%\affiliation{School of Mathematics and Physics, University of Queensland, Brisbane, QLD 4072, Australia}
%\author{S.~Gontcho A Gontcho}
%\affiliation{Department of Physics and Astronomy, University of Rochester, Rochester, NY 14627, USA}
%\author{O.~Graur}
%\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA}
%\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY 10024, USA}
%\affiliation{NSF Astronomy and Astrophysics Postdoctoral Fellow}
%\author{R.~Graziani}
%\affiliation{Universit\'e Clermont Auvergne, CNRS/IN2P3, Laboratoire de
%Physique de Clermont, F-63000 Clermont-Ferrand, France}    
%\author{C.~Harper}
%\affiliation{Physics Division, Lawrence Berkeley National Laboratory, 
%    1 Cyclotron Road, Berkeley, CA, 94720}
%\author{R.~Hlo\u{z}ek}
%\affiliation{Department of Astronomy and Astrophysics, University of Toronto,
%50 St. George Street, Toronto, Ontario, Canada M5S 3H4}
%\affiliation{Dunlap Institute for Astronomy and Astrophysics, University of Toronto, ON, M5S 3H4}
%\author{C.~Howlett}
%\affiliation{International Centre for Radio Astronomy Research, The University of Western Australia, Crawley, WA 6009, Australia}
%\author{D.~Huterer}
%\affiliation{Department of Physics, University of Michigan, 450 Church Street, Ann
%Arbor, MI 48109, USA }
%\author{C.~Ju}
%\affiliation{Physics Division, Lawrence Berkeley National Laboratory, 
%    1 Cyclotron Road, Berkeley, CA, 94720}
%\author{P.-F.~Leget}
%\affiliation{Laboratoire de Physique Nucl\'eaire et de Hautes Energies, Sorbonne Universit\'e, CNRS-IN2P3, 4 Place Jussieu, 75005 Paris, France}    
%\author{E.~V.~Linder}
%\affiliation{Physics Division, Lawrence Berkeley National Laboratory, 
%    1 Cyclotron Road, Berkeley, CA, 94720}
%\author{P.~McDonald}
%\affiliation{Physics Division, Lawrence Berkeley National Laboratory, 
%    1 Cyclotron Road, Berkeley, CA, 94720}
%\author{J.~Nordin}
%\affiliation{Institut fur Physik, Humboldt-Universitat zu Berlin, Newtonstr. 15, 12489 Berlin, Germany}
%\author{P.~Nugent}
%\affiliation{Computational Research Division, Lawrence Berkeley National Laboratory, 
%    1 Cyclotron Road, Berkeley, CA, 94720}\author{S.~Perlmutter}
%\affiliation{Physics Division, Lawrence Berkeley National Laboratory, 
%    1 Cyclotron Road, Berkeley, CA, 94720}
%\affiliation{Department of Physics, University of California Berkeley, 366 LeConte Hall MC 7300, Berkeley, CA, 94720-7300}
%\author{N.~Regnault}
%\affiliation{Laboratoire de Physique Nucl\'eaire et de Hautes Energies, Sorbonne Universit\'e, CNRS-IN2P3, 4 Place Jussieu, 75005 Paris, France}    
%\author{M.~Rigault}
%\affiliation{Universit\'e de Lyon, F-69622, Lyon, France; Universit\'e de Lyon
%1, Villeurbanne; CNRS/IN2P3, Institut de Physique Nucléaire de
%Lyon, France} 
%\author{A.~Shafieloo}
%\affiliation{Korea Astronomy and Space Science Institute, Yuseong-gu, Daedeok-daero 776, Daejeon 34055, Korea}
%\author{A.~Slo\u{z}ar}
%\affiliation{Brookhaven National Laboratory, Physics Department, Upton, NY
%11973, USA} 
%\author{M.~Wood-Vasey}
%\affiliation{PITT PACC, Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, PA 15260, USA} 
%\author{others}

@@

%\begin{abstract}
%In the upcoming decade cadenced wide-field imaging surveys 
%will increase the number of identified  $z<0.3$ Type~Ia supernovae (SNe~Ia)  from the hundreds to the
%hundreds of thousands.  The increase in the number density  and solid-angle coverage 
%of SNe~Ia, in parallel with improvements in the standardization of
%their absolute magnitudes, now make them competitive probes of the growth of structure and hence of gravity.  The peculiar velocity power spectrum
%is sensitive to $\gamma$, which captures the effect of gravity on the linear growth of structure through the relation $f=\Omega_M^\gamma$.
%In the next decade the peculiar velocities of
%SNe~Ia in the local $z<0.3$ Universe will provide a measure of $\gamma$ with as low as
%$0.01$ precision that can definitively distinguish  between General Relativity and leading models of alternative gravity.
%\end{abstract}
